Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-22 paper-webserver.tex
ADD: on BAP

We developed Spfy using continuous integration (CI) techniques: all changes and update to the codebase is automatically ran against a series of tests ensuring functionality and backwards compatibility.
We chose TravisCI \url{travisci.io} which offers free services for open-source projects.
The individual tests use PyTest.

@@

% para: \cite{joensen2014real,thomsen2016bacterial}
% we have a lot of similar directions to this, but just try to make it prettier, more friendly to use, and faster

>>>>

TravisCI \url{travisci.io}, a continuous integration (CI) platform, is integrated into Spfy's Github repository \url{https://github.com/superphy/backend} and runs tests ensuring functionality and backwards compatibility with any changes to the codebase.
The individual tests use PyTest \url{https://doc.pytest.org/} and are run within TravisCI's virtual environment.
The current build status can be checked either on our Gtihub repository or at \url{https://travis-ci.org/superphy/backend}.

@@

% para: \cite{joensen2014real,thomsen2016bacterial}
% we have a lot of similar directions to this, but just try to make it prettier, more friendly to use, and faster
The Bacterial Analysis Platform (BAP), developed out of the Technical University of Denmark, provides and integrated analysis pipeline for bacterial WGS data, as a web service.
BAP is novel in its combined approach to genome analysis as different programs, such as for VF and AMR determination, are included by default into the pipeline; Spfy provides similar functionallity with an expanded focus on integrated result storage and big-data analyses.
In place of a MySQL database for storing the location of result files, Spfy parses result data into graph objects and integrates results into a persistant graph database.
This enables Spfy to create large datasets where analysis results are linked to genomes, and to perform population-wide analyses.
On run-times of analogous algorithmns for prediction tasks, Spfy performs at a similar speed to BAP, though Spfy does not provide genome assembly services.
Spfy also uses a Python-based backend instead of PHP, and Spfy's use of Docker containerization and task queues is a novel as well.
